% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Jonathan D. Terner}
 % Draw a horizontal line the whole width of resume:
 % address begins here
 % Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{16 Kiersted Ave.}
 \moveleft.5\hoffset\centerline{Kingston, NY 12401}
 \moveleft.5\hoffset\centerline{(845) 514-7835 | jon.programming@gmail.com | github.com/Prgrmman}
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}


\begin{resume}
  \vspace{-8mm}
  %%%%%%%%%%%%%%%%%% Education section
    \section{EDUCATION}
    {\sl SUNY Binghamton} \hfill May 2018
   \\Watson School of Engineering, Harpur College of Arts and Sciences.
    \\BS in Computer Science and BA in Mathematical Science.
    % \sl will be bold italic in New Century Schoolbook (or
    % any postscript font) and just slanted in
    %	Computer Modern (default) font
    \begin{itemize}
      \item Cumulative GPA: 3.967
    \end{itemize}
    \vspace{-4mm}
    {\sl Kingston High School} \hfill June 2014
    \begin{itemize}
      \item Valedictorian
    \end{itemize}
    \vspace{-3mm}

    %%%%%%%%%%%%%%%%% Technical Skills section
    \section{TECHNICAL SKILLS}
    \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}
    \vspace{-4mm}
    {\sl Programming}
    \begin{itemize}
      \item Experience focused around object-oriented programming, but also extending to machine learning, shell scripting, functional programming and web design.
    \end{itemize}
    \vspace{-3mm}
    {\sl Languages}
    \begin{itemize}
      \item C, C++, Python, Perl, Java, JavaScript, BASH, Haskell, x86 assembly.
    \end{itemize}
    \vspace{-3mm}
    {\sl Tools and Development}
    \begin{itemize}
      \item Vim, Git, Emacs, GDB, Eclipse, Valgrind, HTML, CSS, \LaTeX, jQuery, SQLite.
    \end{itemize}
    \vspace{-3mm}
    {\sl Operating Systems:} Linux, Windows.

    %%%%%%%%%%%%%%%%%% Experience section 
    \section{EXPERIENCE }
    \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}
    \vspace{-4mm}
    {\sl IBM Spectrum Scale RAID developer} \hfill June 2018 - present
    \vspace{-3mm}

    {\sl Undergraduate Research Assistant} \hfill January-May 2018
    \begin{itemize}
   	  \item National Science Foundation grant recipient
      \item Extensively modifed QEMU/KVM hypervisor to support postcopy live virtual machine migration with added fault tolerance
      \item Advocated for clean, performance-conscious programming practices
      \item Redesigned micro checkpointing algorithm, increasing performance by a factor of 20
    \end{itemize}

    {\sl IBM Specturm Scale Functional Verification Testing Intern} \hfill May-August 2017
    \begin{itemize}
      \item Developed and maintained test software for a distributed clustered file system.
      \item Worked independently designing and implementing test plans.
      \item Actively communicated with development and test team when designing software specifications and writing documentation. 
      \item Administered a distributed Linux cluster.
    \end{itemize}

    \vspace{-2mm}
    {\sl Deerfoot Lodge Staff member(Speculator, NY)} \hfill June-August 2014-2016
    \begin{itemize}
      \item Sous chef: Second-in-command of a commercial kitchen, jointly overseeing a crew of 8 members. Used effective teamwork and interpersonal skills. 
    \end{itemize}


    %%%%%%%%%%%%%%%%% Project section
    \section{PROJECTS}
    \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}
    \vspace{-4mm}
    {\sl Block-Pay}
    \begin{itemize}
      \item Developed group financing software using IBM blockchain technology. Responsible for front end web development and backend development in Node.js
      \item Winning project at the IBM Bluehack hackathon.
    \end{itemize}
    \vspace{-4mm}
    {\sl Cheap-game-finder}
    \begin{itemize}
      \item Used Haskell Cabal to implement libraries for XML and JQuery parsing and API interaction.
    \end{itemize}
    \vspace{-3mm}
    {\sl Word Search Solver}
    \begin{itemize}
      \item Implemented full GUI written in Java that included web browser support.
      \item Featured extensive use and modification of Swing library components.
    \end{itemize}
    \vspace{-3mm}
    {\sl Binary Bomb Lab}
    \begin{itemize}
      \item Rendered C program with hidden functions into x86 assembly.
      \item Used GDB to trace function calls and examine memory to deduce the purposes of the hidden functions.
    \end{itemize}
    \vspace{-3mm}

    %%%%%%%%%%%%%%%%% Honors section
    \section{HONORS}
    \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}
    \vspace{-5mm}
    {\sl Phi Eta Sigma Honor Society.} \hfill October 2015

    %%%%%%%%%%%%%%%%%  Other activities section
    \vspace{-2mm}
    \section{OTHER ACTIVITIES}
    \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}
    \vspace{-4mm}
    Trumpet player for NAfME All Eastern Wind Ensemble. \hfill March 2013

  \end{resume}
\end{document}
